Graphical Tests for Power Comparison of Competing Designs

### 2012-03-28 setup.tex
relationship between three responses

The three response variables are correctness (binary values: correct and wrong),  time taken for answer (skew distribution, log transformation makes it more normal), and confidence level of result, a subjective assessment of correctness of the result, with values 1 (lowest) to 5 (highest).
XXX show figure of response variables: histogram of log time facetted by test fill colour correct
XXX confidence by test, fill by correct

>>>>

The three response variables are correctness (binary values: correct and wrong),  time taken for answer (skew distribution, log transformation makes it more normal), and confidence level of result, a subjective assessment of correctness of the result, with values 1 (lowest) to 5 (highest).
XXX show figure of response variables: histogram of log time facetted by test fill colour correct see figure \ref{fig:time}
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=\linewidth]{time-answer} 
   \caption{Histograms of time taken for answering lineups. On average the Euclidean design is answered faster and with higher power (percentage of correct answers). }
   \label{fig:time}
\end{figure}

XXX confidence by test, fill by correct
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=\linewidth]{conf-answer} 
   \caption{Barcharts of (subjective) confidence in answering correctly for each lineup. A strongly bimodal distribution is apparent, while confidence levels for polar charts are more uniform. There are only slight (and non significant) difference between confidence levels and correctness of results.}
   \label{fig:time}
\end{figure}
